Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-02-28 paper.tex
new changes and addition to section 1 and abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct functioning of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory and sophisticated software modules, in order to meet increasing computational power demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct behavior and compliance with the target system, and supporting new software architectures and legacy designs (usually written in low-level languages). The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

The main difference between embedded systems and CPSs is indeed the strong presence of modern communication technologies ({\it e.g.}, Internet of Things) in the last one. This simple difference causes a revolution in terms of flexibility, scalability, and complexity of those systems and adds a novel class of problems to the already known challenges of embedded systems. For example, micro-grids, {\it i.e.}, small-scale electricity systems that gather different sources of distributed generation (DG) and loads, are emerging CPSs, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. One may also notice that each DG element and the majority of current loads already employ embedded software and present several safety-critical requirements; however, the integration of both constitute a CPS, where additional challenges related to synchronization, stability, control, communication, and reliability of the entire micro-grid arise.

@@

Figure~\ref{intelligent-product} shows some examples of embedded systems, which typically consist of a human-machine interface ({\it e.g.}, keyboard and LCD), a processing unit ({\it e.g.}, real-time computer system), and an instrumentation interface ({\it e.g.}, sensor, network, and actuator) \cite{Kopetz11}. Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may cost civilian lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health and even compromise many aspects of their lives, with serious consequences. One the one hand, portable embedded systems are capable of monitoring and identifying conditions that are very difficult to a physician, mainly when their contact with patients happen only in medical clinics. On the other hand, wrong or diagnostic data may delay necessary treatments or compromise patients' health. 
%
\begin{figure}[!t]
	\centering
	\includegraphics[scale=0.35]{figure1.eps}
	\caption{An embedded system is part of a well-specified larger system (intelligent product).}
	\label{intelligent-product}
\end{figure}

Besides, when physical interaction with the real world is needed, which happens in CPSs, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to the reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models. Specifically, such models can be used to synthesize a given particular system, ensuring that all needed functions are correctly implemented and the correct behavior exhibited, {i.e.}, the system is indeed correct by its method of construction~\cite{Abate17}.

For instance, one may argue that a Linux device driver \cite{ldd} was verified and correctly uses the related kernel services; however, not much can be said about correct access to the associated hardware and its use, {\it i.e.}, if read and write operations are performed according to what is specified in the device's datasheet and setup periods are respected. In summary, the main goal would be ensuring that the developed driver is compliant with the underlying hardware, which goes further than code correctness.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, the increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software domain, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency) must be considered during verification~\cite{Kroening15}. Such observations expand the addressed issues and even complement what was mentioned in the last paragraph.

We cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, and counter-example guided inductive synthesis, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, we describe the main challenges regarding the verification and synthesis of embedded systems, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section \ref{Newapp} then tackles new applications, which take into account the new paradigm addressed here, and Section~\ref{achievements} describes current achievements and future trends in verification and synthesis of embedded systems. Finally, we conclude and describe future work in Section~\ref{conclusions}.

@@

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. \textcolor{red}{nao faltou completeness? talvez fosse bom colocar algumas palavras disso, o que fecharia com BMC e k-induction} Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints.
	\item handling of concurrent software.
	\item platform restrictions.
	\item verification of code pieces or modules that rely on larger structures.
	\item legacy designs. %, which are usually developed with low-level languages.
	\item support to different programming languages, frameworks, and interfaces.
	\item Correct code instrumentation \textcolor{red}{vale a pena mencionar que precisamos instrumentar corretamente o codigo?}.
	\item handling of non-linear and non-convex optimization problems.
\end{enumerate}

@@

\textcolor{red}{serah demais mencionar um framework unificado, que abranja tanto propriedades de bauxo nivel e comportamento quanto descricoes de alto nivel?}
Section~\ref{achievements} outlines contributions toward these research problems.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory and sophisticated software modules, in order to meet increasing computational power and flexibility demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct behavior, providing compliance with the target system, and supporting new software architectures and legacy designs (usually written in low-level languages). The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

The main difference between embedded systems and CPSs is indeed the strong presence of modern communication technologies ({\it e.g.}, Internet of Things - IoT) in the latter. This simple difference causes a revolution in terms of flexibility, scalability, and complexity of those systems and adds a novel class of problems to the challenges found embedded systems domain. For example, micro-grids, {\it i.e.}, small-scale electricity systems that gather different sources of distributed generation (DG) and loads, are emerging CPSs, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. One may also notice that each DG element and the majority of current loads already employ embedded software and present several safety-critical requirements; however, the integration of both constitute a CPS, where additional challenges related to synchronization, stability, control, communication, and reliability of the entire micro-grid arise.

@@

Figure~\ref{intelligent-product} shows some examples of embedded systems, which typically consist of a human-machine interface ({\it e.g.}, keyboard and LCD), a processing unit ({\it e.g.}, real-time computer system), and an instrumentation interface ({\it e.g.}, sensor, network, and actuator) \cite{Kopetz11}. Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may cost civilian lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health and even many aspects of their lives, with serious consequences. On the one hand, portable embedded systems are capable of monitoring and identifying conditions that are very difficult for a physician, mainly when his contact with patients happens only in medical clinics. On the other hand, wrong or incomplete diagnostic data may delay necessary treatments or deteriorate patients' health. 
%
\begin{figure}[!t]
	\centering
	\includegraphics[scale=0.35]{figure1.eps}
	\caption{An embedded system is part of a well-specified larger system (intelligent product).}
	\label{intelligent-product}
\end{figure}

Besides, when physical interaction with the real world is needed, which happens in CPSs, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to the reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models. Specifically, such models can be used to synthesize a given particular system, by ensuring that all needed functions are correctly implemented and the correct behavior is exhibited, {i.e.}, the system is indeed correct by its method of construction~\cite{Abate17}.

For instance, one may argue that a Linux device driver \cite{ldd} was verified and correctly uses the related kernel services; however, not much can be said about correct access to the associated hardware and its use, {\it i.e.}, if read and write operations are performed according to what is specified in the device's datasheet and setup periods are respected. In summary, the main goal would be to ensure that the developed driver is compliant with the underlying hardware, which goes further than code correctness and also tackles the interaction with surrounding entities.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, the increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software domain, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, interfacing, and concurrency) must be considered during verification~\cite{Kroening15}. Such observations expand the addressed issues and even complement what was mentioned in the last paragraphs.

The goals of the present article is to briefly present part of the established research and also clarify the current trends, given that we are on the verge of a paradigm shift, mainly driven by CPSs and IoT. We present a brief discussion about models for CPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, and counter-example guided inductive synthesis, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding the verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section \ref{Newapp} then addresses new applications, which take into account the new paradigm mentioned here, and Section~\ref{achievements} describes current achievements and future trends in verification and synthesis of embedded systems. Finally, we conclude and describe future work in Section~\ref{conclusions}.

@@

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, providing completeness, {\it i.e.},  if all possible states can be reached and evaluated, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints.
	\item handling of concurrent software.
	\item platform restrictions.
	\item verification of code pieces or modules that rely on larger structures.
	\item legacy designs. %, which are usually developed with low-level languages.
	\item support to different programming languages, frameworks, and interfaces.
	\item Correct code instrumentation.
	\item handling of non-linear and non-convex optimization problems.
\end{enumerate}

@@

\textbf{(RP7)} provide a unified framework, which is able to tackle high and low level properties, as well as system behavior, which can lead to another degree of completeness, in such a way that every implementation aspect of an embedded system is addressed and evaluated.

Section~\ref{achievements} outlines contributions toward these research problems.
